#Course : 2 - R Programming
## Quiz 3

### Question 1

Take a look at the 'iris' dataset that comes with R. The data can be loaded with the code:

```{r}
library(datasets)
data(iris)
```


There will be an object called 'iris' in your workspace. In this dataset, what is the mean of 'Sepal.Length' for the species virginica? (Please only enter the numeric result and nothing else.)

**Answers**

```{r}
mean(iris[iris$Species == "virginica",]$Sepal.Length)
```

or using 'tapply' to calculate the mean of 'Sepal.Length' within each species:

```{r}
tapply(iris$Sepal.Length,iris$Species, mean)
```

- tapply(the vector were the function f will be apply, the factor variable, function f)

### Question 2

Continuing with the 'iris' dataset from the previous Question, what R code returns a vector of the means of the variables 'Sepal.Length', 'Sepal.Width', 'Petal.Length', and 'Petal.Width'?

**Answers**


apply(iris, 1, mean) -> "Vector with NA";

apply(iris, 2, mean) -> "Warning messages: 1: In mean.default(newX[, i], ...) : "argument is not numeric or logical: returning NA";

colMeans(iris) -> "Error in colMeans(iris) : 'x' must be numeric";

```{r}
apply(iris[, 1:4], 2, mean)
```


**Explanation:**

- ?apply => Returns a vector or array or list of values obtained by applying a function to margins of an array or matrix.
- apply(X, MARGIN, FUN, ...)
- X an array, including a matrix.
- MARGIN a vector giving the subscripts which the function will be applied over. E.g., for a matrix 1 indicates rows, 2 indicates columns, c(1, 2) indicates rows and columns.
- FUN the function to be applied
- apply(iris[, 1:4], 2, mean)
- Select the columns from 1 to 4 [, 1:4], grup by columns (2) and applies on each column the function mean (apply (..., mean))
- Sepal.Length  Sepal.Width Petal.Length  Petal.Width 
-   5.843333     3.057333     3.758000     1.199333 

### Question 3

Load the 'mtcars' dataset in R with the following code:

```{r}
library(datasets)
data(mtcars)
```

There will be an object names 'mtcars' in your workspace. You can find some information about the dataset by running:

```{r}
?mtcars
```

How can one calculate the average miles per gallon (mpg) by number of cylinders in the car (cyl)?

**Answers**

- apply(mtcars, 2, mean) "Wrong, this will make the mean for each column"
- lapply(mtcars, mean)   "Wrong, this will make the mean for each column"
- with(mtcars, tapply(mpg, cyl, mean)) => "Correct"
- tapply(mtcars$cyl, mtcars$mpg, mean) => "Wrong, tapply(mtcars$mpg,mtcars$cyl, mean) would be correct"

**Explanation**

- with(mtcars, tapply(mpg, cyl, mean))
-       4        6        8 
- 26.66364 19.74286 15.10000 
- "The with is being used because we are using the varibles mpg, cyl of the environment"
- "tapply(mtcars\$mpg,mtcars\$cyl, mean) would also work"

###Question 4
Continuing with the 'mtcars' dataset from the previous Question, what is the absolute difference between the average horsepower of 4-cylinder cars and the average horsepower of 8-cylinder cars?

**Explanation:**

- x4 <- mtcars[,"cyl"] == 4
- x8 <- mtcars[,"cyl"] == 8
- abs(mean(mtcars[,"hp"][x4]) - mean(mtcars[,"hp"][x8]))
- [1] 126.5779
- or
- abs(tapply(mtcars\$hp,mtcars\$cyl==4,mean)[2] - tapply(mtcars\$hp,mtcars\$cyl==8,mean)[2])


###Question 5
If you run
 
> debug(ls)

what happens when you next call the 'ls' function?

**Answers**

- The 'ls' function will return an error.
- You will be prompted to specify at which line of the function you would like to suspend execution and enter the browser.
- Execution of the 'ls' function will suspend at the 4th line of the function and you will be in the browser.
- Execution of 'ls' will suspend at the beginning of the function and you will be in the browser.

**Explanation:**
- Execution of 'ls' will suspend at the beginning of the function and you will be in the browser.


