#Course : 2 - R Programming
## Quiz 1

###Introduction
This first quiz will check your ability to execute basic operations on objects in R and to understand some basic concepts. For questions 11-20 you will need to load a dataset into R and do some basic manipulations in order to answer the questions on the quiz.

You may want to print a copy of the quiz questions to look at as you work on the assignment. It is recommended that you save your answers as you go in the event that a technical problem should occur with your network connection or computer. Ultimately, you must submit the quiz online to get credit!

###Data
The zip file containing the data for questions 11-20 in this Quiz can be downloaded [here](https://d396qusza40orc.cloudfront.net/rprog%2Fdata%2Fquiz1_data.zip):

### Week 1 Quiz Data
For this assignment you will need to unzip this file in your working directory.

### Question 1

The R language is a dialect of which of the following programming languages?

**Answer:**

- C             [x];
- Lisp          [x];
- S             [v];
- Fortran       [x].

**Explanation**
R is a dialect of the S language which was developed at Bell Labs.

### Question 2

The definition of free software consists of four freedoms (freedoms 0 through 3). Which of the following is NOT one of the freedoms that are part of the definition?

- The freedom to study how the program works, and adapt it to your needs.       [x];             	
- The freedom to run the program, for any purpose.                              [x];
- The freedom to prevent users from using the software for undesirable purposes.[v];
- The freedom to redistribute copies so you can help your neighbor.             [x].

**Explanation**
This is not part of the free software definition. Freedom 0 requires that the users of free software be free to use the software for any purpose.

### Question 3

In R the following are all atomic data types EXCEPT:

**Answers:**

- data frame    [v];
- numeric       [x];
- logical       [x];
- character     [x];

**Explanation**
'data frame' is not an atomic data type in R.

### Question 4
If I execute the expression x <- 4 in R, what is the class of the object 'x' as determined by the 'class()' function?

**Answers:**

- complex       [x];
- real          [x];
- numeric       [v];
- list          [x];

**Explanation**
```{r}
x <- 4
class(x)

```

### Question 5

What is the class of the object defined by the expression x <- c(4, "a", TRUE)?

**Answers:**

- character     [v];
- logical       [x];
- numeric       [x];
- integer       [x].

**Explanation**

R does automatic coercion of vectors so that all elements of the vector are the same data class. The character class is the "lowest common denominator" here and so all elements will be coerced into that class.

```{r}
x <- c(4, "a", TRUE)
class(x)
```

### Question 6

If I have two vectors x <- c(1,3, 5) and y <- c(3, 2, 10), what is produced by the expression cbind(x, y)?

**Answers:**

- a 2 by 2 matrix                       [x];
- a 2 by 3 matrix                       [x];
- a matrix with 2 columns and 3 rows    [v];
- a vector of length 3                  [x].

**Explanation**

The 'cbind' function treats vectors as if they were columns of a matrix. It then takes those vectors and binds them together column-wise to create a matrix.

```{r}
x <- c(1,3, 5)
y <- c(3, 2, 10)
cbind(x, y)
```

### Question 7

A key property of vectors in R is that:

**Answers:**

- elements of a vector can be of different classes              [x];
- elements of a vector can only be character or numeric         [x];
- a vector cannot have have attributes like dimensions          [x];
- elements of a vector all must be of the same class            [v].

### Question 8

Suppose I have a list defined as x <- list(2, "a", "b", TRUE). What does x[[1]] give me?

**Answers:**
- a character vector containing the element "2".        [x];
- a list containing the letter "a".                     [x];
- a list containing the number 2.                       [x];
- a numeric vector of length 1.                         [v].

**Explanation:**

x[[1]] holds the element 2. Therefore "a numeric vector of length 1".


```{r}
x <- list(2, "a", "b", TRUE)

x[[1]]

class(x[[1]])
```


### Question 9

Suppose I have a vector x <- 1:4 and y <- 2:3. What is produced by the expression x + y?

**Answers**

- an integer vector with the values 3, 5, 3, 4  [x];
- an error;                                     [x];
- an integer vector with the values 3, 5, 5, 7  [v];
- an numeric vector with the values 3, 5, 5, 7  [v].

x + y = (1 + 2, 2 + 3, 3 + 2, 4 + 3)

**Explanation**

```{r}
x <- 1:4
y <- 2:3

x + y
```


### Question 10

Suppose I have a vector x <- c(3, 5, 1, 10, 12, 6) and I want to set all elements of this vector that are less than 6 to be equal to zero. What R code achieves this?

**Answers**

- x[x == 6] <- 0       "Wrong, this will replace the number 6 for zero"
- x[x == 0]            "Wrong, this will give a vector with all the elements of x that are equal to zero"
- x[x %in% 1:5] <- 0   "Right, this will set all elements of x with values between 1 and 5 to zero."
- x[x != 6] <- 0        "Wrong, this will set all elements of x that are different than 6 to zero"."

### Question 11

In the dataset provided for this Quiz, what are the column names of the dataset?

**Answers**

- 1, 2, 3, 4, 5, 6
- Month, Day, Temp, Wind
- Ozone, Solar.R, Wind, Temp, Month, Day
- Ozone, Solar.R, Wind

**Explanation**

- x <- read.csv(file="hw1_data.csv",head=TRUE,sep=",") "Read quiz1 data"
- names(x) => [1] "Ozone"   "Solar.R" "Wind"    "Temp"    "Month"   "Day"


### Question 12

Extract the first 2 rows of the data frame and print them to the console. What does the output look like?

**Answers**

>  Ozone Solar.R Wind Temp Month Day    [x]

> 1     9      24 10.9   71     9  14

> 2    18     131  8.0   76     9  29

> Ozone Solar.R Wind Temp Month Day     [x]

> 1     7      NA  6.9   74     5  11

> 2    35     274 10.3   82     7  17

>  Ozone Solar.R Wind Temp Month Day    [x]

> 1    18     224 13.8   67     9  17

> 2    NA     258  9.7   81     7  22

> Ozone Solar.R Wind Temp Month Day     [v]

> 1    41     190  7.4   67     5   1

> 2    36     118  8.0   72     5   2

**Explanation**

> The data was read on the previous question 'x'
> x[1:2,] => Gives the first two rows

>   Ozone Solar.R Wind Temp Month Day

> 1    41     190  7.4   67     5   1

> 2    36     118  8.0   72     5   2


### Question 13

How many observations (i.e. rows) are in this data frame?

**Answers**

- 129   [x];
- 45    [x];
- 153   [v];
- 160   [x].

**Explanation**

nrow(x) => 153

### Question 14
Extract the last 2 rows of the data frame and print them to the console. What does the output look like?

> Ozone Solar.R Wind Temp Month Day     [x]

> 152    34     307 12.0   66     5  17

> 153    13      27 10.3   76     9  18

> Ozone Solar.R Wind Temp Month Day     [x]

> 152    11      44  9.7   62     5  20

> 153   108     223  8.0   85     7  25

>  Ozone Solar.R Wind Temp Month Day    [v]

> 152    18     131  8.0   76     9  29

> 153    20     223 11.5   68     9  30

> Ozone Solar.R Wind Temp Month Day     [x]

> 152    31     244 10.9   78     8  19

> 153    29     127  9.7   82     6   7

**Explanation**

> The `tail()' function is an easy way to extract the last few elements of an R object.
> tail(x,2) => Takes the last two elements of x

>     Ozone Solar.R Wind Temp Month Day

> 152    18     131  8.0   76     9  29

> 153    20     223 11.5   68     9  30


### Question 15
What is the value of Ozone in the 47th row?

**Answers:**

- 63    [x]
- 18    [x]
- 21    [v]
- 34    [x]

**Explanation**
> x\$Ozone[47] => 21

### Question 16

How many missing values are in the Ozone column of this data frame?

**Answers:**

- 9     [x]
- 43    [x]
- 37    [v]
- 78    [x]

**Explanation:**

- The `is.na' function can be used to test for missing values.
- sum(is.na(x\$Ozone)) => [1] 37
- is.na gives a vector of boolean were TRUE means missing value, using function sum
- TRUE will count as 1 and FALSE as zero. Thus, sum(is.na(x\$Ozone)) gives the number
- of missing values in the Ozone column

### Question 17

What is the mean of the Ozone column in this dataset? Exclude missing values (coded as NA) from this calculation.

**Answers:**

- 42.1  [v]
- 53.2  [x]
- 18.0  [x]
- 31.5  [x]

**Explanation:**
- The `mean' function can be used to calculate the mean.
- mean(x\$Ozone,na.rm =T) => 42.12931
- na.rm a logical value indicating whether NA values should be stripped before the computation proceeds.

### Question 18
Extract the subset of rows of the data frame where Ozone values are above 31 and Temp values are above 90. What is the mean of Solar.R in this subset?


**Answers:**

- 205.0         [x]
- 334.0         [x]
- 185.9         [x]
- 212.8         [v]

**Explanation:**

- We need to construct a logical vector in R to match the question's requirements. Then use that logical vector to subset the data frame.
- logVec <- x\$Temp > 90 & x\$Ozone > 31 "Contructing the logical vector"
- mean(x\$Solar.R[logVec],na.rm=T) => 212.8

### Question 19
What is the mean of "Temp" when "Month" is equal to 6?

**Answers:**

- 75.3          [x]
- 85.6          [x]
- 79.1          [v]
- 90.2          [x]

**Explanation:**

- mean(x\$Temp[x\$Month == 6]) => 79.1
- x\$Month == 6 gives a logical vector with True when the  Month == 6 and false otherwise.
- x\$Temp[x\$Month == 6] gives all the rows of the column Temp where Month == 6.

### Question 20
What was the maximum ozone value in the month of May (i.e. Month = 5)?

**Answers:**

- 100   [x]
- 18    [x]
- 115   [v]
- 97    [x]

**Explanation:**

max(x\$Ozone[x\$Month == 5],na.rm=T)


