#Course : 2 - R Programming
## Quiz 2

### Question 1

Suppose I define the following function in R
```{r}
cube <- function(x, n) 
{
        x^3
}
```

What is the result of running:

```{r}
cube(3)
```

in R after defining this function?

**Answers**

- An error is returned because 'n' is not specified in the call to 'cube' [x];
- The number 27 is returned [v];
- The users is prompted to specify the value of 'n' [x];
- A warning is given with no value returned [x].

**Explanation**

Because 'n' is not evaluated, it is not needed even though it is a formal argument.


### Question 2

The following code will produce a warning in R.

```{r}
x <- 1:10
if(x > 5) 
{
        x <- 0
}
```

**Answers**

- 'x' is a vector of length 10 and 'if' can only test a single logical statement [v];
- There are no elements in 'x' that are greater than 5 [x];
- You cannot set 'x' to be 0 because 'x' is a vector and 0 is a scalar [x];
- The expression uses curly braces [x].

### Question 3

Consider the following function:

```{r}
f <- function(x) 
{
        g <- function(y) 
        {
                y + z
        }
        z <- 4
        x + g(x)
}
```

If I then run in R: 

```{r}
z <- 10
f(3)
```

**Answers**

What value is returned?

- 10 [v];
- 7  [x];
- 6  [x];
- 4  [x].

**Explanation:**

- f(3)
- z = 4
- 3 + g(3)
- 3 + (3 + 4)
- 10


### Question 4:

Consider the following expression:

```{r}
x <- 5
y <- if(x < 3) {
        NA
} else {
        10
}
```

**Answers**

What is the value of 'y' after evaluating this expression?

- 10 [v];
- 5  [x];
- 3  [x];
- NA [x].

** Explanation:**

> x = 5
> y = (if (5 < 3) NA else 10)
> y = 10


### Question 5

Consider the following R function

```{r}

h <- function(x, y = NULL, d = 3L) 
{
        z <- cbind(x, d)
       
        if(!is.null(y))
                z <- z + y
        else
                z <- z + f
        
        g <- x + y / z
        
        if(d == 3L)
                return(g)
        g <- g + 10
        g
}
```

**Answers**

Which symbol in the above function is a free variable?

- f [v];
- z [x] -> "Is a local variable";
- d [x] -> "Is a argument variable";
- L [x] -> "Represents long"
- g [x] -> "Is a local variable";

### Question 6

What is an environment in R?

**Answers**

- collection of symbol/value pairs [v];
- a list whose elements are all functions [x];
- an R package that only contains data [x];
- a special type of function [x].

### Question 7

The R language uses what type of scoping rule for resolving free variables?

**Answers**

- lexical scoping [v];
- dynamic scoping [x];
- global scoping  [x];
- compilation scoping [x].

### Question 8

How are free variables in R functions resolved?

**Answers**

- The values of free variables are searched for in the environment in which the function was defined [v];
- The values of free variables are searched for in the global environment [x];
- The values of free variables are searched for in the working directory [x];
- The values of free variables are searched for in the environment in which the function was called [x].

### Question 9

What is one of the consequences of the scoping rules used in R?

**Answers**

- All objects must be stored in memory [v];
- All objects can be stored on the disk [x];
- Functions cannot be nested [x];
- R objects cannot be larger than 100 MB [x].

### Question 10

In R, what is the parent frame?

**Answers**

- It is always the global environment [x];
- It is the environment in which a function was defined [x];
- It is the package search list [x];
- It is the environment in which a function was called [v].


